DNSKEY Management

### 2012-12-04 paper/paper.tex
Improve introduction

\section{Introduction}
%% TODO add some blah about management and penetration.

In the following, every necessary operation for key management in
DNSSEC is described as a reminder to the reader.

>>>>

\section{Introduction}
DNSSEC is gradually being deployed in the Internet. However, managing
the cryptographic keys required for the secure delegation provided by
DNSSEC is not always entirely trivial.

In this paper we will first remind of the prinicpal necessary
operations for key management in DNSSEC. Then we will give the reader
an overview of the current status of DNSSEC deployment in the Internet
to put the in-detail discussion about key management into the right
context.

Finally, we will shortly outline the DNSSEC situation in Switzerland
(i.e. the \verb|ch.|  and how its authorities handle DNSKEY management
issues.

\subsection{Operations}
In the following, every necessary operation for key management in
DNSSEC is described as a reminder to the reader. This is by no means
intended to give an introduction to DNSSEC but rather to remind the
reader about specific details particularily relevant to this paper.
